---
title       : House Sale Prediction Application
subtitle    : 
author      : Jonas Wiorek
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Predict House Sale Price 

If you are on the market to buy a house or sale your house, this application 
offers a prediction of the value of the house. It is based on a statistical
model. The model is using data from house sales including the sale price, living square feet, number of bedrooms, number of bathrooms and many other data on the house including location. 

The first version of the model is a linear model based on living sqft, number of bedrooms and number of bathrooms. Later version will enhance the prediction model taking for instance the location into account.  

---

## House Sale Prediction 

A simple linear regression model is used to predict the price of a house located 
in the U.S. The variates used in the model are living square feetm number of bedrooms and number of bathrooms   

$price = \beta_0 + \beta_1livingSqft + \beta_2NoOfBeds + \beta_3NoOfBaths$   
```{r, echo=FALSE}
beta0 <- 74847.14
beta1 <- 309.3924
beta2 <- -57860.89 
beta3 <- 7932.713
```
The values of the model weights are:   
$\beta_0 =$ `r format(round(beta0,0), scientific = FALSE)`   
$\beta_1 =$ `r format(round(beta1,0), scientific = FALSE)`   
$\beta_2 =$ `r format(round(beta2,0), scientific = FALSE)`   
$\beta_3 =$ `r format(round(beta3,0), scientific = FALSE)`   

Note that $\beta_2$ is negative. Thus, giving the same number of living square 
feet and number of bathrooms, the predicted house price is lower the more bedrooms.

---

## Square Meter to Square Feet Conversion

```{r, echo=FALSE}
library(ggplot2)
beta1 <- 10.7639
sm <- 0:1000

sf <- beta1*sm

qplot(sm,sf)

```

---

## Bath Definition

- Full bathroom - Containing four plumbing fixtures: bathtub, shower, toilet, and sink
- 3/4 bath - Containing toilet, sink, and shower
- Half (1/2) bath - Containing a toilet and sink




